---
knitr:
  opts_chunk:
    fig.width: 12
    fig.height: 6
---

{{< pagebreak >}}
\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

```{r init}

pkgs <- c("magrittr", "targets")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2)

```

# Results

## Dot plots

### Time-series on a weekly interval

```{r, fig.width = 14, fig.height = 8}

tar_read(plt_dot_diff_week)[[1]]
tar_read(plt_dot_diff_week)[[2]]
tar_read(plt_dot_diff_week)[[3]]
tar_read(plt_dot_diff_week)[[4]]

```

{{< pagebreak >}}

## Autocorrelation plots

### Exploring seasonality within the number of medication claims (month) {#sec-nclaim-month}

```{r}

tar_read(plt_acf_diff_month)[[1]]
tar_read(plt_pacf_diff_month)[[1]]

```

### Exploring seasonality within the claim-to-patient ratio (month) {#sec-ratio-month}

```{r}

tar_read(plt_acf_diff_month)[[3]]
tar_read(plt_pacf_diff_month)[[3]]

```

### Exploring seasonality within the eigenvector centrality (month) {#sec-eigen-month}

```{r}

tar_read(plt_acf_diff_month)[[4]]
tar_read(plt_pacf_diff_month)[[4]]

```

{{< pagebreak >}}
\KOMAoptions{paper=portrait,pagesize}
\recalctypearea

## Polar Plots

### Number of claim

```{r}

tar_read(plt_polar_n_claim)

```

{{< pagebreak >}}

### Claim-to-patient ratio

```{r}

tar_read(plt_polar_claim2patient)

```

{{< pagebreak >}}

### Eigenvector centrality

```{r}

tar_read(plt_polar_eigen)

```
