---
knitr:
  opts_chunk:
    fig.width: 14
    fig.height: 8
---

```{r init}

pkgs <- c("magrittr", "targets")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2, scipen = 999)

```

\uselandscape

# Results on seasonality analysis {#sec-seasonality}

::: {.content-visible when-profile="seasonality"}

## Dot plots

### Differenced time-series on a daily interval

```{r}

tar_read(plt_dot_diff_day)[-5]

```

### Differenced time-series on a weekly interval

```{r}

tar_read(plt_dot_diff_week)[[1]]
tar_read(plt_dot_diff_week)[[2]]
tar_read(plt_dot_diff_week)[[3]]
tar_read(plt_dot_diff_week)[[4]]

```

### Differenced time-series interval on a monthly interval

```{r}

tar_read(plt_dot_diff_month)[-5]

```

{{< pagebreak >}}

## Autocorrelation and periodic plots

:::

### Exploring seasonality within the number of medication claims (day) {#sec-nclaim-day}

```{r}

tar_read(plt_period_day)[[1]]
tar_read(plt_acf_diff_day)[[1]]
tar_read(plt_pacf_diff_day)[[1]]

```

::: {.content-visible when-profile="seasonality"}

### Exploring seasonality within the number of patients (day) {#sec-npat-day}

```{r}

tar_read(plt_period_day)[[2]]
tar_read(plt_acf_diff_day)[[2]]
tar_read(plt_pacf_diff_day)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (day) {#sec-ratio-day}

```{r}

tar_read(plt_period_day)[[3]]
tar_read(plt_acf_diff_day)[[3]]
tar_read(plt_pacf_diff_day)[[3]]

```

:::

### Exploring seasonality within the eigenvector centrality (day) {#sec-eigen-day}

```{r}

tar_read(plt_period_day)[[4]]
tar_read(plt_acf_diff_day)[[4]]
tar_read(plt_pacf_diff_day)[[4]]

```

### Exploring seasonality within the number of medication claims (week) {#sec-nclaim-week}

```{r}

tar_read(plt_period_week)[[1]]
tar_read(plt_acf_diff_week)[[1]]
tar_read(plt_pacf_diff_week)[[1]]

```

::: {.content-visible when-profile="seasonality"}

### Exploring seasonality within the number of patients (week) {#sec-npat-week}

```{r}

tar_read(plt_period_week)[[2]]
tar_read(plt_acf_diff_week)[[2]]
tar_read(plt_pacf_diff_week)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (week) {#sec-ratio-week}

```{r}

tar_read(plt_period_week)[[3]]
tar_read(plt_acf_diff_week)[[3]]
tar_read(plt_pacf_diff_week)[[3]]

```

:::

### Exploring seasonality within the eigenvector centrality (week) {#sec-eigen-week}

```{r}

tar_read(plt_period_week)[[4]]
tar_read(plt_acf_diff_week)[[4]]
tar_read(plt_pacf_diff_week)[[4]]

```

### Exploring seasonality within the number of medication claims (month) {#sec-nclaim-month}

```{r}

tar_read(plt_period_month)[[1]]
tar_read(plt_acf_diff_month)[[1]]
tar_read(plt_pacf_diff_month)[[1]]

```

::: {.content-visible when-profile="seasonality"}

### Exploring seasonality within the number of patients (month) {#sec-npat-month}

```{r}

tar_read(plt_period_month)[[2]]
tar_read(plt_acf_diff_month)[[2]]
tar_read(plt_pacf_diff_month)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (month) {#sec-ratio-month}

```{r}

tar_read(plt_period_month)[[3]]
tar_read(plt_acf_diff_month)[[3]]
tar_read(plt_pacf_diff_month)[[3]]

```

:::

### Exploring seasonality within the eigenvector centrality (month) {#sec-eigen-month}

```{r}

tar_read(plt_period_month)[[4]]
tar_read(plt_acf_diff_month)[[4]]
tar_read(plt_pacf_diff_month)[[4]]

```

\normalpapersize
