---
knitr:
  opts_chunk:
    fig.width: 12
    fig.height: 8
---

```{r init}

pkgs <- c("targets", "magrittr")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

```

# Results

## Descriptive analysis

In this section,

{{< pagebreak >}}

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

### Time-series on a daily interval

```{r, fig.width = 14}

tar_read(plt_dot_day)[[1]]
tar_read(plt_dot_day)[[2]]
tar_read(plt_dot_day)[[3]]
tar_read(plt_dot_day)[[4]]

```

{{< pagebreak >}}

### Time-series on a weekly interval

```{r, fig.width = 14}

tar_read(plt_dot_week)[[1]]
tar_read(plt_dot_week)[[2]]
tar_read(plt_dot_week)[[3]]
tar_read(plt_dot_week)[[4]]

```

{{< pagebreak >}}

### Time-series on a monthly interval

```{r, fig.width = 14}

tar_read(plt_dot_month)[[1]]
tar_read(plt_dot_month)[[2]]
tar_read(plt_dot_month)[[3]]
tar_read(plt_dot_month)[[4]]

```

{{< pagebreak >}}

### Exploring seasonality within the number of medication claims (day) {#sec-nclaim-day}

```{r}

tar_read(plt_acf_day)[[1]]
tar_read(plt_pacf_day)[[1]]

```

### Exploring seasonality within the number of patients (day) {#sec-npat-day}

```{r}

tar_read(plt_acf_day)[[2]]
tar_read(plt_pacf_day)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (day) {#sec-ratio-day}

```{r}

tar_read(plt_acf_day)[[3]]
tar_read(plt_pacf_day)[[3]]

```

### Exploring seasonality within the eigenvector centrality (day) {#sec-eigen-day}

```{r}

tar_read(plt_acf_day)[[4]]
tar_read(plt_pacf_day)[[4]]

```

### Exploring seasonality within the number of medication claims (week) {#sec-nclaim-week}

```{r}

tar_read(plt_acf_week)[[1]]
tar_read(plt_pacf_week)[[1]]

```

### Exploring seasonality within the number of patients (week) {#sec-npat-week}

```{r}

tar_read(plt_acf_week)[[2]]
tar_read(plt_pacf_week)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (week) {#sec-ratio-week}

```{r}

tar_read(plt_acf_week)[[3]]
tar_read(plt_pacf_week)[[3]]

```

### Exploring seasonality within the eigenvector centrality (week) {#sec-eigen-week}

```{r}

tar_read(plt_acf_week)[[4]]
tar_read(plt_pacf_week)[[4]]

```

### Exploring seasonality within the number of medication claims (month) {#sec-nclaim-month}

```{r}

tar_read(plt_acf_month)[[1]]
tar_read(plt_pacf_month)[[1]]

```

### Exploring seasonality within the number of patients (month) {#sec-npat-month}

```{r}

tar_read(plt_acf_month)[[2]]
tar_read(plt_pacf_month)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (month) {#sec-ratio-month}

```{r}

tar_read(plt_acf_month)[[3]]
tar_read(plt_pacf_month)[[3]]

```

### Exploring seasonality within the eigenvector centrality (month) {#sec-eigen-month}

```{r}

tar_read(plt_acf_month)[[4]]
tar_read(plt_pacf_month)[[4]]

```
